Testing Theories of Expectation Formation using Probabilistic Forecasts

### 2019-06-26 paper/Draft.tex
The discussion of FE and RV efficiency results are outlined.The implication for IR results remain to be written down.

In Table \ref{NullTestTable}, I reproduce a number of commonly used tests of null hypothesis of FIRE replying on differnet specific implications discussed in the previous section. I first reproduce the results from two papers, \cite{mankiw2003disagreement} and \cite{fuhrer2018intrinsic} and then proceed to show the results with the additional restrictions from ucnertainty.

@@

The second batch of tests focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \cite{nordhaus1987forecasting}. In particular, I follow the model specifications in \cite{fuhrer2018intrinsic}. According to FIRE, rational forecast revision only responds to newly realized shocks thus it cannot be predicted by past information. For the same reason, regression coefficient of forecast for $y_{t+h}$  at time $t+1$ on that at $t-1$ is exactly equal to $1$, implying one-to-one responses.  A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future.

>>>>

In Table \ref{NullTestTable}, I reproduce a number of commonly used tests of null hypothesis of FIRE replying on differnet specific implications discussed in the previous section mostly following \cite{mankiw2003disagreement}.

@@

 The second batch of tests focus on  forecasting efficiency utilizing revision across different vintages of forecasts in the spirit of \cite{nordhaus1987forecasting} and \cite{fuhrer2018intrinsic}. In particular, I follow the model specifications in \cite{fuhrer2018intrinsic}. According to FIRE, rational forecast revision only responds to newly realized shocks thus it cannot be predicted by past information. For the same reason, regression coefficient of forecast for $y_{t+h}$  at time $t+1$ on that at $t-1$ is exactly equal to $1$, implying one-to-one responses.  A weaker test in the similar test is that the change in mean forecast from one period to the next one fixing forecasting horizon is serially correlated to an greater extent than that comes from the additional period in far future.

The weak efficiency tests use change in forecast and uncertainty instead of revisions. This is not a direct test of the null of FIRE as we have discussed that the rigidity models do not have direct testable predictions about the change in forecast and uncertainty with fixed forecast horizon. But in the same time, the auto regression features do speak to the persistence of the forecasts over the time horizon. In particular, if the individual forecasts and their uncertainty turn out to be persisent over different horizons, this implies that the agent does not react to the news and newly realized shocks enough.
